A data-intensive assessment of the species-abundance distribution.

### 2015-04-15 defense_pres.tex
Condenses example slides.
Tweaks.
Shrinks one figure that was running off the edge.
Moves open science slide to the end.
Swaps slides, changes picture.
Rearranges slide.
Changes pictures to more realistic example beetle SAD.

\section{Introduction}
\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/BeetleRAD.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Species abundance distribution}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\note{
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

\begin{frame}
\frametitle{Pattern \& process.}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Reveals pattern-generating mechanisms of community structure.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
\end{center}
\end{frame}

@@

\subsubsection{Data Collection}
\begin{frame}[t]{}
\frametitle{Abundance database}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances (counts).
\item Complete sampling.
\item Raw data (not heavily processed).
\item High degree of taxonomic resolution.
\item Observational.
\end{itemize}
\end{frame}

@@

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/dissertation/likelihoods_one_to_one.png}
\end{frame}

>>>>

\section{Introduction}
\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.25]{./sad-data/dissertation/BeetleRAD.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Let's begin with an example...}
\begin{center}
\includegraphics[scale=.25]{./sad-data/dissertation/BeetleRAD_w_graph.png}\\
\end{center}
\end{frame}

\begin{frame}
\frametitle{Pattern \& process.}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
\end{center}
\begin{itemize}
\item Reveals pattern-generating mechanisms of community structure.
\end{itemize}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

@@

\subsubsection{Data Collection}
\begin{frame}[t]{}
\frametitle{Abundance database}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances (counts).
\item Complete sampling.
\item Raw data (not heavily processed).
\item Observational.
\end{itemize}
\end{frame}

@@

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.43]{./sad-data/dissertation/likelihoods_one_to_one.png}
\end{frame}
